\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-09-20 gwnnDraft02.tex
drafting and references

The recent experimental detection of gravitational waves~\cite{Abbott:2016blz} gives humanity a new way to observe the universe. Future experiments~\cite{Crowder:2005nr,Harry:2006fi,Sathyaprakash:2012jk,2017arXiv170200786A,Seto:2001qf,Sato:2017dkf,Janssen:2014dka} will greatly expand the frequency range observable. Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Caprini:2015zlo,Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Mazumdar:2018dfl}. Thus searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis. 
Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation. This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Breitbach:2018ddu,Bertone:2019irm,Caputo:2019wsd,Helmboldt:2019pan,Fairbairn:2019xog,Bai:2018dxf,Baldes:2018emh,Croon:2018erz,Geller:2018mwu,Heikinheimo:2018esa,Aoki:2017aws,Bernal:2017kxu,Acharya:2017szw,Tsumura:2017knk,Dienes:2016vei,Hardy:2016mns,Addazi:2016fbj,Jaeckel:2016jlh}. 
In this work, we explore the possibility of having multiple decoupled hidden sectors. Large numbers of hidden sectors can solve the hierarchy problem as in the Dvali Redi model~\cite{Dvali:2009ne} or in the more recently explored $N$naturalness~\cite{Arkani-Hamed:2016rle} framework, or in the orbifold Higgs models (maybe?\cite{}). They can also be motivated by dark matter considerations (dynamical dark matter? others?). 

@@

In general, the multi-hidden sector models explored here feature feature of huge number of (nearly) massless degrees of freedom. Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and baryons of these sectors can also be relativistic. In $N$naturalness this feature is realized quite dramatically: each of the $N$ of sectors possess relativistic degrees of freedom. The presence of these particles can have two main effects: extra relativistic particles can alter the expansion history of the universe through changes to the energy density or hidden sectors can feature annihilations that reheat the photons or neutrinos of our sector near Big Bang Nucleosynthesis (BBN) and affect the light element abundances. The effective number of neutrino species, $N_{eff}$, is impacted by these contributions and, as such, is the strictest constraint that must be dealt with when studying these type of multi-phase transition models. 

@@

We now turn to the gravitational wave signatures of our setup. At high temperatures, each of the hidden sectors has QCD in the quark/gluon phase, but at temperatures around $\Lambda_{\rm QCD,i}$, the sector undergoes a phase transition into the hadronic phase, where we compute $\Lambda_{\rm QCD,i}$ for the different sectors in Sec.~\ref{sec:dQCD}. As discussed in that section, this phase transition will be strongly first order (SFOPT) for certain numbers of light degrees of freedom, which will generate gravitational waves. This differs from QCD within the SM sector, as the PT is a crossover and not first order~\cite{Fodor:2001pe}.

@@

A SFOPT proceeds through bubble nucleation, where bubbles of the hadronic phase form in the vacuum of the quark phase. These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.  These bubbles are described by the following Euclidean action~\cite{Linde:1981zj}
%
\begin{equation}\label{eqn:EuclideanAction}
S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg],
\end{equation}
where the time component has been integrated out due to nucleation occuring, not in vaccum, but in a finite temperature plasma. $\phi$ is the symmetry breaking scalar field with a non-zero VEV. In the case of the chiral phase transition, the scalar field breaking the SU$(6)_{R}$ $ \times$ SU$(6)_{L}$ chiral symmetry is the effective quark condensate $\phi_{i} \sim \langle q\bar{q} \rangle_{i}$ of the respective sector. We leave the thermalized potential $V(\phi, T)$ general., as previous stated, an exact QCD potential at the time of the chiral phase transition is not well understood outside of lattice results. Some authors~\cite{Bai:2018dxf} have used the chiral effective Lagrangian to calculate a low energy thermalized potential for confining SU$(N)$.

The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves. Assuming that the SM sector is radiation dominated, A quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation ~\citep{Espinosa:2010hh} ,
\begin{equation}
\alpha     \equiv  \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30},
\label{eq:alpha}
\end{equation}
with $\epsilon$ being calculable from the scalar potential. Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  the latent head, $\epsilon$ should correspond to the energy density of the hidden sector going through the PT. The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) is the number of relativistic degrees of freedom at the time of the phase transition, with contributions from species in both the visible and dark sectors. It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
\begin{equation}\label{eqn:RelaDOF}
g_{*} = g_{*,\gamma} + \sum_{i} g_{*,i} (\xi_{i})^4
\end{equation}
with $\xi$ being the temperature ratio defined in Eq.~(\ref{eq:xi}). The bounds from effective number of neutrinos ~\citep{} mean that $\xi_i \lesssim 1$ for all $i$, so $g_{*} \approx g_{*,\gamma}$. In the case of dark QCD-like chiral  phase transitions, the temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{QCD,i})$. Authors \citep{Bai:2018dxf} who have looked at calculating $\alpha$ through the low energy effective chiral Lagrangian have found various upper bounds. We take the optimistic scenario where the numerator is bounded above by the symmetry breaking scale, 
%
\begin{equation}
\alpha_i \approx \xi_i^{4} \approx \bigg( \frac{\Lambda_{QCD,i}}{T_{\gamma}^{nuc}}\bigg)^4
\end{equation}
%
where $T_{\gamma}^{nuc}$ is the temperature of the SM photon bath at the time of the phase transition. Another important parameter to characterize the phase transition is its inverse timescale, $\beta$ ~\citep{Caprini:2015zlo}. The inverse timescale can be calculated using the action in Eq.~(\ref{eqn:EuclideanAction}),

@@

Due to the lack of an analytic potential, we take $\beta/H$ to be a standard value currently seen in the field. There has been a lot of work in recent years in the estimation of $\beta/H$ using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models~\citep{Helmboldt:2019pan}. Although, these studies claim a large range of values and thus a consenes has yet been reached.
\subsection{Production of Gravitational Waves}
\label{sec:signals}

Gravitational waves are produced with contributions from different components of the SFOPT's evolution.  It is commonplace to parameterize the spectral energy density in gravitational waves   by $\Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{\textrm{d} \rho_{\textrm{GW}}(f) }{\textrm{dlog}(f)}$ \citep{PhysRevD.75.043507}, where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density to not over close the universe. The three leading order contributions to the GW power spectrum are as follows:
\begin{itemize}
\item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration. With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$~\citep{PhysRevD.45.4514, Huber_2008}. 
\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves. With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$~\citep{PhysRevLett.112.041301}.
\item \textbf{Magnetohydrodynamical contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves. With efficiency factor $\kappa_{
turb} \approx 0.1 \kappa_{v} $~\citep{PhysRevD.74.063521}.
\end{itemize}

Where $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$. Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh}, 
\begin{equation}\label{eqn:critPTstrength}
\alpha_{\infty} = \frac{(T^{nuc}_h)^2}{\rho_R}\left[\sum_{bosons} n_i\frac{\Delta m^2_i}{24} + \sum_{fermions} n_i\frac{\Delta m_i^2}{48}\right],
\end{equation} 
for particles with $n_i$ degrees of freedom that obtain mass through the phase transition. 
Exotic sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.

@@

Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime. Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$). In this case, the efficiency factors for sound wave and MHD contributions tend to zero and the GWs produced are purely from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.  The form of the GW power spectrum at the time of nucleation is given by ~\citep{Breitbach:2018ddu},

\begin{equation}
h^2\Omega_{\textrm{GW}}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
\end{equation}
Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles. $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
\begin{equation}\label{eqn::spectralshape}
S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}
\end{equation}
The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.  The various hidden sectors can phase transition at different scales and therefore temperatures, causing a shift in the GW spectrum's peak frequency given by~\cite{Huber_2008},

\begin{equation}
f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}}
\end{equation}

Where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}) , although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant. Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT. In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$. As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{\textrm{GW}}^{*}(f)$, will redshift to today's value $\Omega_{\textrm{GW}}^{0}(f) = \mathcal{A}\, \Omega_{\textrm{GW}}^{*}((a_{0}/a) f) $. The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837},

\begin{equation}\label{eqn::redshifting}
\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2
\end{equation}
where $a$ ($a_{0}$)  and $H$ ($H_{0}$) are the scale factor and Hubble constant at the time of nucleation (observation), respectfully. Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW signal that would be measured today is given by the coherent sum,
\begin{equation}
\Omega_{\textrm{GW}}^{0} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{\textrm{GW}}^{i,*}((a_{0}/a)_{i} f) 
\end{equation}
It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within $N$natrualness or other decoupled hidden sector models. In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar. This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.

\begin{figure}[h!]
\centering
\includegraphics[scale=.3]{Nnatral.png} 
\caption{ Gravitational wave power spectrum for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}. All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
\label{fig::Nnatural}
\end{figure}
Applying this to the standard reheating scenario of $N$natrualness, introduced in~\ref{sec:reheat}, we get GW signals as seen in figure~(\ref{fig::Nnatural}). Plotted are the individual contributions to the signal from each phase transitioned sector, as well as the coherent sum of all sectors. Future GW interferometers and pulsar timing array sensitivity curves are shown in comparison to the signal. The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, more detail in the construction of these curves is given in the following section. Notice that the total signal is dominated by the first sectors contribution. This is caused by the quartic temperature ratio suppression in Eq. (\ref{eq:alpha}) and the large temperature gaps between adjacent sectors. Such a suppression leads to standard $N$natrualness evading future detector thresholds by a few orders of magnitude in units of energy density. This is not the case if we neglect the standard reheaton scenario and consider the more generalized reheating scenarios of section~\ref{sec:constraints}.

Assuming all else equal, we use the temperature schemes from Eq. (\ref{eqn:energyDensityAllowed}) to produce the plots in figure~(\ref{fig:Haa}). In all cases, the summed GW signal is detectable by one or more proposed interferometers. The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors. As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.  This is seen in figure~(\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum. The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature). Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.

@@

\subsection{Detection of Stochastic Graviational Waves}

>>>>

The recent experimental detection of gravitational waves~\cite{Abbott:2016blz} gives humanity a new way to observe the universe. Future experiments~\cite{Seto:2001qf,Crowder:2005nr,Harry:2006fi,Sathyaprakash:2012jk,Janssen:2014dka,2017arXiv170200786A,Sato:2017dkf} will greatly expand the frequency range observable. Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Caprini:2015zlo,Mazumdar:2018dfl}. Thus searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis. 
Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation. This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Jaeckel:2016jlh,Addazi:2016fbj,Hardy:2016mns,Dienes:2016vei,Tsumura:2017knk,Acharya:2017szw,Bernal:2017kxu,Aoki:2017aws,Heikinheimo:2018esa,Geller:2018mwu,Croon:2018erz,Baldes:2018emh,Bai:2018dxf,Breitbach:2018ddu,Fairbairn:2019xog,Helmboldt:2019pan,Caputo:2019wsd,Bertone:2019irm}. 
In this work, we explore the possibility of having multiple decoupled hidden sectors. Large numbers of hidden sectors can solve the hierarchy problem as in the Dvali Redi model~\cite{Dvali:2009ne}, in the more recently explored $N$naturalness~\cite{Arkani-Hamed:2016rle} framework, or in orbifold Higgs models~\cite{Craig:2014aea,Craig:2014roa}. They can also be motivated by dark matter considerations~\cite{Dienes:2011ja,Dienes:2011sa,Dienes:2016vei}. 

@@

In general, the multi-hidden sector models explored here feature feature of huge number of (nearly) massless degrees of freedom. Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and baryons \draftnote{can't have quarks and baryons} of these sectors can also be relativistic. In $N$naturalness this feature is realized quite dramatically: each of the $N$ of sectors possess relativistic degrees of freedom. The presence of these particles can have two main effects: extra relativistic particles can alter the expansion history of the universe through changes to the energy density or hidden sectors can feature annihilations that reheat the photons or neutrinos of our sector near Big Bang Nucleosynthesis (BBN) and affect the light element abundances. The effective number of neutrino species, $N_{eff}$, is impacted by these contributions and, as such, is the strictest constraint that must be dealt with when studying these type of multi-phase transition models. 

@@

We now turn to the gravitational wave signatures of our setup. At high temperatures, each of the hidden sectors has QCD in the quark/gluon phase, but at temperatures around $\Lambda_{\rm QCD,i}$, the sector undergoes a phase transition into the hadronic phase, where we compute $\Lambda_{\rm QCD,i}$ for the different sectors in Sec.~\ref{sec:dQCD}. As discussed in that section, this phase transition will be strongly first order (SFOPT) for certain numbers of light quarks, which will generate gravitational waves. This differs from QCD in the SM sector, as the PT is a crossover and not first order~\cite{Fodor:2001pe}.

@@

A SFOPT proceeds through bubble nucleation, where bubbles of the hadronic phase form in the vacuum of the quark phase. These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.  These bubbles are described by the following Euclidean action~\cite{Linde:1981zj}
%
\begin{equation}\label{eqn:EuclideanAction}
S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg],
\end{equation}
where the time component has been integrated out due to nucleation occuring, not in vaccum, but in a finite temperature plasma. $\phi$ is the symmetry breaking scalar field with a non-zero VEV. In the case of the chiral phase transition, the scalar field breaking the SU$(N_f)_{R}$ $ \times$ SU$(N_f)_{L}$ chiral symmetry is the effective quark condensate $\phi_{i} \sim \langle q\bar{q} \rangle_{i}$ of the respective sector. We leave the thermalized potential $V(\phi, T)$ general. As previously stated, an exact QCD potential at the time of the chiral phase transition is not well understood outside of lattice results. In~\cite{Bai:2018dxf} chiral effective Lagrangian was used to calculate a low energy thermalized potential for confining SU$(N)$.

The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves. Assuming that the SM sector is radiation dominated, a quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation~\citep{Espinosa:2010hh} ,
\begin{equation}
\alpha     \equiv  \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30},
\label{eq:alpha}
\end{equation}
with $\epsilon$ being calculable from the scalar potential. Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  the latent head, $\epsilon$ should correspond to the energy density of the hidden sector going through the PT. The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) is the number of relativistic degrees of freedom at the time of the phase transition, with contributions from species in both the visible and dark sectors. It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
\begin{equation}\label{eqn:RelaDOF}
g_{*} = g_{*,\gamma} + \sum_{i} g_{*,i} (\xi_{i})^4
\end{equation}
with $\xi$ being the temperature ratio defined in Eq.~(\ref{eq:xi}). The bounds from effective number of neutrinos ~\citep{} mean that $\xi_i \lesssim 1$ for all $i$, so $g_{*} \approx g_{*,\gamma}$. In the case of dark QCD-like chiral  phase transitions, the temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{QCD,i})$. The work of~\citep{Bai:2018dxf} calculated $\alpha$ with an effective chiral Lagrangian have found various upper bounds. We take the optimistic scenario where the numerator is bounded above by the symmetry breaking scale, 
%
\begin{equation}
\alpha_i \approx \xi_i^{4} \approx \bigg( \frac{\Lambda_{QCD,i}}{T_{\gamma}^{nuc}}\bigg)^4
\end{equation}
%
where $T_{\gamma}^{nuc}$ is the temperature of the SM photon bath at the time of the phase transition. Another important parameter to characterize the phase transition is its inverse timescale, $\beta$~\citep{Caprini:2015zlo}. The inverse timescale can be calculated using the action in Eq.~(\ref{eqn:EuclideanAction}),

@@

Due to the lack of an analytic potential, we take $\beta/H$ to be a standard value currently seen in the field~\cite{}. There has been a lot of work in recent years in the estimation of $\beta/H$ using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models~\citep{Helmboldt:2019pan}. \draftnote{Are there other papers? One paper is not a lot of work}. Although, these studies claim a large range of values and thus a consensus has \draftnote{not?} yet been reached.
\subsection{Production of Gravitational Waves}
\label{sec:signals}

Gravitational waves are produced with contributions from different components of the SFOPT's evolution.  It is commonplace to parameterize the spectral energy density in gravitational waves by~\citep{PhysRevD.75.043507} 
\begin{equation}
\Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{d \rho_{\textrm{GW}}(f) }{d \textrm{\,log}(f)} , 
\end{equation}
where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density. The three leading order contributions to the GW power spectrum are as follows:
\begin{itemize}
\item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration. With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$~\citep{PhysRevD.45.4514, Huber_2008}. 
\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves. With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$~\citep{PhysRevLett.112.041301}.
\item \textbf{Magnetohydrodynamical contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves. With efficiency factor $\kappa_{
turb} \approx 0.1 \kappa_{v} $~\citep{PhysRevD.74.063521}.
\end{itemize}

Where $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$. Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh}, 
\begin{equation}\label{eqn:critPTstrength}
\alpha_{\infty} = \frac{(T^{nuc}_h)^2}{\rho_R}\left[\sum_{bosons} n_i\frac{\Delta m^2_i}{24} + \sum_{fermions} n_i\frac{\Delta m_i^2}{48}\right],
\end{equation} 
for particles with $n_i$ degrees of freedom that obtain mass through the phase transition. 
Exotic sectors feature no baryons \draftnote{why??} and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness \draftnote{isn't that what we're talking about?}\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.

@@

Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime. Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$). In this case, the efficiency factors for sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.  The form of the GW power spectrum at the time of nucleation is given by~\citep{Breitbach:2018ddu},

\begin{equation}
h^2\Omega_{\textrm{GW}}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
\end{equation}
\draftnote{Why is there a * on the $\Omega$?} Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles. $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
\begin{equation}\label{eqn::spectralshape}
S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}
\end{equation}
The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.  The various hidden sectors can phase transition at different scales and therefore temperatures, causing a shift in the GW spectrum's peak frequency given by~\cite{Huber_2008},
%
\begin{equation}
f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
\end{equation}
%
where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}) , although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.

Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT. In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$. As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{\textrm{GW}}^{*}(f)$, will redshift to today's value $\Omega_{\textrm{GW}}^{0}(f) = \mathcal{A}\, \Omega_{\textrm{GW}}^{*}((a_{0}/a) f) $. The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837},

\begin{equation}\label{eqn::redshifting}
\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2
\end{equation}
where $a$ ($a_{0}$)  and $H$ ($H_{0}$) are the scale factor and Hubble constant at the time of nucleation (observation), respectfully. Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW signal that would be measured today is given by the coherent sum,
\begin{equation}
\Omega_{\textrm{GW}}^{0} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{\textrm{GW}}^{i,*}((a_{0}/a)_{i} f) 
\end{equation}
It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within $N$natrualness or other decoupled hidden sector models.\draftnote{what?} In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar. This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.

\begin{figure}[h!]
\centering
\includegraphics[scale=.3]{Nnatral.png} 
\caption{ Gravitational wave power spectrum for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}. All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green). \draftnote{The sum curve and the i=5 curve aren't visible.}  }
\label{fig::Nnatural}
\end{figure}
Applying this to the standard reheating scenario of $N$natrualness, introduced in~\ref{sec:reheat}, we get GW signals as seen in figure~(\ref{fig::Nnatural}). Plotted are the individual contributions to the signal from each phase transitioned sector, as well as the coherent sum of all sectors. Future GW interferometers and pulsar timing array sensitivity curves are shown in comparison to the signal. The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, more detail in the construction of these curves is given in Section~\ref{sec:detection}. Notice that the total signal is dominated by the first sectors contribution. This is caused by the quartic temperature ratio suppression in Eq.~(\ref{eq:alpha}) and the large temperature gaps between adjacent sectors. Such a suppression leads to standard $N$natrualness evading future detector thresholds by a few orders of magnitude in units of energy density. This is not the case if we consider the more generalized reheating scenarios of section~\ref{sec:constraints}.

\draftnote{I think we need more details on the scenarios that go into making those plots.} Assuming all else equal, we use the temperature schemes from Eq.~(\ref{eqn:energyDensityAllowed}) to produce the plots in figure~(\ref{fig:Haa}). In all cases, the summed GW signal is detectable by one or more proposed interferometers. The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors. As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.  This is seen in figure~(\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum. The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature). Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.

@@

\subsection{Detection of Stochastic Graviational Waves}
\label{sec:detection}
